Chatbots in the classroom: an analysis from the teacher's perspective

### 2021-05-21 edubots_surveys.Rnw
Adds telegram frequencies and changes perc. in text refs #13

According to the results summarized in Fig. \ref{figure:chatbots_use_gender_age_exp}, there are no significant differences between male and female teachers. Regarding the instant messaging apps, teachers mainly use Whatsapp (40\%-50\%), the most popular messaging app in Spain. Similar numbers are shown for the use of the app provided by their institutions, Universities or Education System Administration. Finally, about 20\% use Telegram. The distribution of messaging apps per age are not significant for the Whatsapp and apps provided by their institutions. However, younger teachers use also Telegram with more than 25\%, a percentage that falls to about 10\% for teachers that are 55 or older. The third column compares the use of these apps considering the number of years of experience. One interesting result is that, contrarily to the idea of technology adaptation issues when considering older teachers, about 65\% of teachers with more than 25 years of experience use the platforms provided by their institutions while the percentage goes down to less than 50\% for teachers with 6-15 years of experience.

>>>>

According to the results summarized in Fig. \ref{figure:chatbots_use_gender_age_exp}, teachers mainly use the instant messaging app provided by their institutions (55\%),  and Whatsapp (44\%), the most popular messaging app in Spain. Finally, about 20\% also use Telegram. 
Although gender differences are not significant, female teachers answered they use instant messaging apps more than male teachers (about 10\% more). Also, teachers in vocational Education also use Whatsapp more than university teachers.

With respect to the distribution of the use of messaging apps per age, there are no significant differences for the Whatsapp and apps provided by their institutions. However, younger teachers use also Telegram with more than 25\%, a percentage that falls to about 10\% for teachers that are 55 or older. The third column compares the use of these apps considering the number of years of experience. One interesting result is that, contrarily to the idea of technology adaptation issues when considering older teachers, about 65\% of teachers with more than 25 years of experience use the platforms provided by their institutions while the percentage goes down to less than 50\% for teachers with 6-15 years of experience.
